RDF Validation of Metadata \\ on Person-Level and Aggregated Data

### 2015-03-02 paper/paper7/paper7-appendix.tex
4.2

\begin{itemize}
	\item \textbf{{\em DISCO-C-DATA-PROPERTY-FACETS-01:}} The abstract of a study (\emph{disco:purpose}) should have a minimum length (\emph{xsd:minInclusive}) of x. 
\end{itemize}

>>>>

\begin{itemize}
	\item \textbf{{\em DISCO-C-DATA-PROPERTY-FACETS-01:}} The abstract of a study (\emph{disco:purpose}) should have a minimum length (\emph{xsd:minLength}) of x. 
\end{itemize}

### 2015-03-02 paper/paper7/paper7.tex
4.2

For more detailed analyses, researchers refer to person-level data from which aggregated data is derived from, 
as person-level data include additional variables needed for further research.
%Although not that common, the other direction is also possible, 
%i.e. researchers may use metadata on person-level data to search for aggregated data.
One very common example for detailed analyses on person-level data is the content-driven comparison of multiple studies.
Researchers get promising findings (in form of published tables with a few columns) within a metadata portal leading to subsequent research questions 
like 'How to compare the unemployment rate of different countries (e.g. Germany, UK, and France) in the last 10 years grouped by age?'.
The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific study are theoretically comparable and can therefore be used to answer the underlying research question.
Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger}, or by a code list including multiple age clusters (such as '0 to 10' and '11 to 20'). 
To determine if variables measuring \emph{age} 
- collected within multiple studies of different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
are comparable, both content-driven and technology-driven validation is performed either
within our developed validation environment or by matching algorithms. 
An example for a content-driven validation is to investigate if variables are represented in a compatible way,
i.e. are the variables' code lists theoretically comparable.
Technically, it can be validated (1) if variable definitions are available, (2) if code lists are properly structured, and (3) if for each code an associated category (a human-readable label) is specified.

@@

\textbf{Metadata on Person-Level Data in RDF.}
For a broader view of the data framework and more detailed analyses we refer to the metadata on person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}} 
and publicly provided by the \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}}.
\emph{Missy} is an online service platform that provides systematically structured metadata for official statistics on European person-level data sets. This includes data documentation at the study and variable level as well as documentation materials, tools and further information. 
Aggregated (qb:DataSet) and underlying person-level data sets (\emph{disco:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
The aggregated variable \emph{formal childcare} is calculated on the basis of six person-level variables like 
\emph{Education at pre-school}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC/2011/Cross-sectional/original#2011-Cross-sectional-RL010}}.
%(2) Education at compulsory school,
%(3) Child care at centre-based services,
%(4) Child care at day-care centre,
%(5) Child care by a professional child-minder, and
%(6) Child care by grand-parents, household members, relatives, friends, neighbours.
For each person-level variable detailed metadata is given (definitions and descriptions, theoretical concepts, underlying questions, code lists, frequencies and descriptive statistics, countries, year of data collection, classifications) enabling researchers to replicate the results shown in the aggregated data tables from Eurostat.
Metadata on person-level data is represented in RDF using the \emph{Disco} vocabulary.
The series (\emph{disco:StudyGroup}) \emph{EU-SILC} contains (\emph{disco:inGroup}) one study (\emph{disco:Study}) for each year (\emph{dcterms:temporal}) of data collection, e.g. \emph{EU-SILC 2011}.   
The property \emph{dcterms:spatial} points to the countries (\emph{dcterms:Location} resources which are the same as \emph{GeoNames} resources representing these countries) for which the data has been collected.
The study \emph{EU-SILC 2011} contains (\emph{disco:product}) eight person-level data sets (\emph{disco:LogicalDataSet}).
Data sets include (\emph{disco:variable}) person-level variables (\emph{disco:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
Metadata on person-level data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
One common research question is ,e.g., the comparison of variables like 
\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).

@@

\textbf{Studies.}
A \emph{study} represents the process by which a data set was generated or collected.
Each study must have an abstract ({\emph{R-46: data property facets}), or if the abstract is missing, a title (\emph{R-71: conditional properties}).

@@

It is useful to declare properties to be conditional, i.e. if particular properties exist, then specific other properties must also be present (\emph{R-71: conditional properties}).
If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
then the property {\em disco:isValid} has to be stated indicating if the code is valid (\emph{true}) or missing (\emph{false}).
%\footref{R-71-CONDITIONAL-PROPERTIES}

>>>>

For more detailed analyses, researchers refer to person-level data from which aggregated data is derived from, 
as person-level data include additional variables needed for further research.
%Although not that common, the other direction is also possible, 
%i.e. researchers may use metadata on person-level data to search for aggregated data.
One very common example for detailed analyses on person-level data is the content-driven comparison of multiple studies.
Researchers get promising findings (in form of published tables with a few columns) within a metadata portal leading to subsequent research questions 
like 'How to compare the unemployment rate of different countries (e.g. Germany, UK, and France) in the last 10 years grouped by age?'.
The first step is to determine in which countries the unemployment rate is collected and which other variables of each country-specific study are theoretically comparable and can therefore be used to answer the underlying research question.
A \emph{study} represents the process by which a data set was generated or collected.
Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger}, or by a code list including multiple age clusters (such as '0 to 10' and '11 to 20'). 
To determine if variables measuring \emph{age} 
- collected within multiple studies of different countries (\emph{$age_{DE}$}, \emph{$age_{UK}$}) - 
are comparable, both content-driven and technology-driven validation is performed either
within our developed validation environment or by matching algorithms. 
An example for a content-driven validation is to investigate if variables are represented in a compatible way,
i.e. are the variables' code lists theoretically comparable.
Technically, it can be validated (1) if variable definitions are available, (2) if code lists are properly structured, and (3) if for each code an associated category (a human-readable label) is specified.

@@

\textbf{Metadata on Person-Level Data in RDF.}
For a broader view of the data framework and more detailed analyses we refer to the metadata on person-level data collected for the series \emph{EU-SILC (European Union Statistics on Income and Living Conditions)}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC}} 
and publicly provided by the \emph{Microdata Information System (MISSY)}\footnote{\url{http://www.gesis.org/missy/eu/missy-home}}.
Where data collection is cyclic, data sets may be released as a \emph{series}, 
where each cycle of the data collection activity produces one or more data sets. 
\emph{Missy} is an online service platform that provides systematically structured metadata for official statistics on European person-level data sets. This includes data documentation at the study and variable level as well as documentation materials, tools and further information. 
Aggregated (qb:DataSet) and underlying person-level data sets (\emph{disco:LogicalDataSet}) are connected by \emph{prov:wasDerivedFrom}. 
The aggregated variable \emph{formal childcare} is calculated on the basis of six person-level variables like 
\emph{Education at pre-school}\footnote{\url{http://www.gesis.org/missy/eu/metadata/EU-SILC/2011/Cross-sectional/original#2011-Cross-sectional-RL010}}.
%(2) Education at compulsory school,
%(3) Child care at centre-based services,
%(4) Child care at day-care centre,
%(5) Child care by a professional child-minder, and
%(6) Child care by grand-parents, household members, relatives, friends, neighbours.
For each person-level variable detailed metadata is given (definitions and descriptions, theoretical concepts, underlying questions, code lists, frequencies and descriptive statistics, countries, year of data collection, classifications) enabling researchers to replicate the results shown in the aggregated data tables from Eurostat.
Metadata on person-level data is represented in RDF using the \emph{Disco} vocabulary.
The series (\emph{disco:StudyGroup}) \emph{EU-SILC} contains (\emph{disco:inGroup}) one study (\emph{disco:Study}) for each year (\emph{dcterms:temporal}) of data collection, e.g. \emph{EU-SILC 2011}.   
The property \emph{dcterms:spatial} points to the countries (\emph{dcterms:Location} resources which are the same as \emph{GeoNames} resources representing these countries) for which the data has been collected.
The study \emph{EU-SILC 2011} contains (\emph{disco:product}) eight person-level data sets (\emph{disco:LogicalDataSet}).
Data sets include (\emph{disco:variable}) person-level variables (\emph{disco:Variable}) like the six ones needed to calculate the aggregated variable \emph{formal childcare}.
Metadata on person-level data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
One common research question is ,e.g., the comparison of variables like 
\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).

@@

\textbf{Studies.}
For datatype properties it should be possible to declare frequently needed \emph{facets} to drive user interfaces and validate input against simple conditions, including min/max values, regular expressions, and string length ({\emph{R-46: data property facets}).
Each study must have an abstract, i.e., the abstract (\emph{disco:purpose}) should have a minimum length (\emph{xsd:minLength}) of 0.
It is useful to declare properties to be conditional, i.e., if particular properties exist (or do not exist), then specific other properties must also be present (\emph{R-71: conditional properties}).
If the abstract of a study is missing, a title has to be stated.

@@

 (\emph{R-71: conditional properties}).
If a {\em skos:Concept} represents a code (having a {\em skos:notation} property) and a category (having a {\em skos:prefLabel} property), 
then the property {\em disco:isValid} has to be stated indicating if the code is valid (\emph{true}) or missing (\emph{false}).
%\footref{R-71-CONDITIONAL-PROPERTIES}
